\section{Project Plan}

Figure~\ref{flow} shows the overview of the proposed framework.

The project plan (illustrated in figure~\ref{fig:workPlan}) is described below

\textbf{Project Proposal (Weeks 1-7)}:
\begin{itemize}
\item Researching, performing a feasibility study, and writing up this report.
\end{itemize}

\textbf{Implementation (Weeks 8-24)}: 
\begin{itemize}
\item \textbf{Weeks 8-14} Implement the EDSL, which encapsulates the vector type transformations, supports
      a rudimentary cost model, as well as including variants for describing how to parallelize
      maps and folds. Also implement the ability to interpret the EDSL from Idris, this can
      be helpful for testing while creating the framework, as well as for
      testing programs before converting them onto a FPGA.

\item \textbf{Weeks 15-19} Implement generating all possible program variants from a given program,
      if possible use Idris with the vector type transformation properties to prove
      that variants will always generate the same results as the original program.

\item \textbf{Weeks 20-22} Implement a flexible interface for exporting the EDSL into IR formats.

\item \textbf{Weeks 23-24} If the project is not running on schedule this time can be allocated to catching up.
Due to Idris not having a stable release the codebase may need to be updated if there are breaking changed,
or it may take some time to overcome an issue due to bugs in the implementation. If on schedule, this time
can be allocated into adding new features, or improving the implementation.
\end{itemize}

\textbf{Project Writeup + Presentation (Weeks 25-28)}
\begin{itemize}
\item This time is dedicated to writing up the project paper and preparing 
the presentation.
\end{itemize}





\begin{figure*}
    \begin{ganttchart}[vgrid, x unit=0.47cm, y unit chart=0.5cm]{1}{28}
        \gantttitle{Academic Weeks}{28} \\
		\gantttitle{Semester 1}{13} \gantttitle{Semester 2}{15} \\
        \gantttitlelist{1,...,28}{1} \\
		\ganttgroup{Project Proposal}{1}{7} \\
		\ganttbar{Background Reading}{1}{2} \\
		\ganttbar{Feasibility Study}{3}{5} \\
		\ganttlinkedbar{Proposal Writeup}{6}{7} \\
		\ganttmilestone{Project Proposal Complete}{7} \\
		\ganttgroup{Implementation}{8}{24} \\
		\ganttbar{EDSL implementation}{8}{14} \\
		\ganttbar{Program Variant Generation}{15}{19} \\
		\ganttbar{IR Interface}{20}{22} \\
		\ganttbar{Slack Time}{23}{24} \\
		\ganttmilestone{Implementation Complete}{24} \\
		\ganttbar{Project Writeup + Presentation}{25}{28}
		

		\ganttlink{elem1}{elem2}
 	 	\ganttlink{elem2}{elem3}
		\ganttlink{elem3}{elem4}	
		\ganttlink{elem4}{elem6}	
        \ganttlink{elem6}{elem7}
        \ganttlink{elem7}{elem8}
        \ganttlink{elem8}{elem9}
        \ganttlink{elem9}{elem11}
    \end{ganttchart}
    \caption{Project Schedule as Gantt Chart}
    \label{fig:workPlan}
\end{figure*}
